### 2021-03-30 rebuttal.txt

We are grateful for the attention and care the reviewers took when considering our paper.

Response to Review 1
--------------------

- An obvious question is how is this work related to the work and methods used for Enigma?

ENIGMA-NG [9] differs from our neural precedence recommender (NPR) significantly in that it deals with a different task (given clause selection),
it assumes a common signature across the problems
and it uses a recursive neural network (a more restrictive NN architecture).
ENIGMA Anonymous [Jakubuv 2020] uses the graph neural network (GNN) architecture proposed in [25], and the relation of our work to this architecture is outlined in section 6.
In more detail, NPR deals with the task of proposing good symbol precedences, while ENIGMA solves given clause selection (an instance of clause classification).
NPR is trained on a proxy task of precedence pair classification,
while ENIGMA is trained directly on the task of clause classification.
ENIGMA uses a lossy hypergraph encoding,
while we use a lossless graph encoding with only binary edges,
which allows our architecture to match the standard R-GCN as proposed in [31] more closely.

### 2021-03-30 rebuttal.txt

- An obvious question is how is this work related to the work and methods used for Enigma?

ENIGMA-NG [9] differs from our neural precedence recommender (NPR) significantly in that it deals with a different task (given clause selection),
it assumes a common signature across the problems
and it uses a recursive neural network (a more restrictive NN architecture).
ENIGMA Anonymous [Jakubuv 2020] uses the graph neural network (GNN) architecture proposed in [25], and the relation of our work to this architecture is outlined in section 6.
In more detail, NPR deals with the task of proposing good symbol precedences, while ENIGMA solves given clause selection (an instance of clause classification).
NPR is trained on a proxy task of precedence pair classification,
while ENIGMA is trained directly on the task of clause classification.
ENIGMA uses a lossy hypergraph encoding,
while we use a lossless graph encoding with only binary edges,
which allows our architecture to match the standard R-GCN as proposed in [31] more closely.

- Despite the clear improvement over baseline, the percentage gained does not appear
to be too big. It is possible, that the potential effect of better orderings is not
too high, regardless of the optimizations. Can you give some insights for this
line of thought?

The impact of symbol precedence on the proof search is limited,
especially in case it is only used as a tie-breaker in the regular KBO.
While using the TKBO for literal ordering observably increases the impact of the predicate precedence on the proof search,
the impact remains indirect and thus it is expected to be relatively limited compared to,
e.g., given clause selection.
[FB: Try to estimate how much learning precedences can help by summarizing the results on random precedences.]

### 2021-03-30 rebuttal.txt

We are very grateful for the attention and care the reviewers took when considering our paper.

@@

- You don't describe how many "incomplete" precedence pairs you
have, e.g. pair where one precedence leads to a proof, the other
to a timeout.

[FB: I'll try to extract this from the data. Most likely this information is not available.]

- If I understand you correctly, the graph representation of a problem is fixed. So why don't you filter before generating training examples?

We agree that filtering the problems first by the graph representation size would make the procedure clearer.
The procedure described in the paper was used mainly because it allowed cheaper tuning of the hyperparameters that control the conversion to graphs –
in most of the experiments, we only need to convert a small part of the training and test problems,
and determining whether a graph representation of a problem has at most 100 000 nodes requires performing the conversion to graph.
Filtering by the graph size before splitting into training and test set, once the hyperparameters are tuned, seems to be a reasonable improvement.

### 2021-03-31 rebuttal.txt

- An obvious question is how is this work related to the work and methods used for Enigma?

ENIGMA-NG [9] differs from our neural precedence recommender (NPR) significantly in that it deals with a different task (given clause selection),
it assumes a common signature across the problems
and it uses a recursive neural network (a more restrictive NN architecture).
ENIGMA Anonymous [Jakubuv 2020] uses the graph neural network (GNN) architecture proposed in [25], and the relation of our work to this architecture is outlined in section 6.
In more detail, NPR deals with the task of proposing good symbol precedences, while ENIGMA solves given clause selection (an instance of clause classification).
NPR is trained on a proxy task of precedence pair classification,
while ENIGMA is trained directly on the task of clause classification.
ENIGMA uses a lossy hypergraph encoding,
while we use a lossless graph encoding with only binary edges,
which allows our architecture to match the standard R-GCN as proposed in [31] more closely.

- Despite the clear improvement over baseline, the percentage gained does not appear
to be too big. It is possible, that the potential effect of better orderings is not
too high, regardless of the optimizations. Can you give some insights for this
line of thought?

It is incredibly difficult to estimate in absolute terms, how large an improvement
one could in our setting on TPTP achieve using some form of "perfect orderings".
However, experiments with random precedences [7] showed that the prover perceptibly responds 
to changes of this parameter and that work on a recommender is worthwhile.

----------- Response to Review 2 -----------

@@

- How does your tool behave in the presence of theories (assuming AVATAR is used)?

Both in the training and in the evaluation, AVATAR was disabled and we didn't consider problems with theories.
Although, in principle, theory symbols could be subject to our recommender, Vampire treats them differently than the rest  
when constructing a precedence and we did not want to be sidetracked by these specificities.

@@

- Now Vampire can also handle higher-order problems. Can your technique also improve Vampire's performance in this context?

Again, this seems in principle possible, as long as the ordering used by the HO vampire still relies on a precedence,
but we did not investigate the details yet.

@@

In this experiment, we have not attempted to control nor analyze the similarity between the problems in the training and test sets.
Splitting the problem set by the domain or the source of the problems is, however, an interesting idea.

----------- Response to Review 3 -----------

- Why do you use the number or iterations of the main loop?

We mainly selected this metric because it is deterministic
and can be measured while other processes are making the computer busy.
Wall-clock time is more sensitive to the compute environment 
and more care needs to be taken to obtain meaningful commeasureable across multiple runs.
However, the point raised by the reviewer is valid and suggests that using wall clock time as the decisive metric,
if implemented well, may increase the performance of the trained system.

### 2021-03-31 rebuttal.txt

----------- Response to Review 3 -----------

- Why do you use the number or iterations of the main loop?

We mainly selected this metric because it is deterministic
and can be measured while other processes are making the computer busy.
Wall-clock time is more sensitive to the compute environment 
and more care needs to be taken to obtain meaningful commeasureable across multiple runs.
However, the point raised by the reviewer is valid and suggests that using wall clock time as the decisive metric,
if implemented well, may increase the performance of the trained system.

- If I understand you correctly, the graph representation of a problem is fixed. So why don't you filter before generating training examples? CPU time must be cheap! ;-)

We chose to generate the training and validation examples (in the form of oriented pairs of precedences) independently from the graph representation of the problems.
This allowed us to adjust the hyperparameters of the two processes (example generation and graph representation) independently,
keeping the computation cost of the graph representation hyperparameter tuning relatively low.

### 2021-03-31 rebuttal.txt

We are very grateful for the attention and care the reviewers took when considering our paper.

----------- Response to Review 1 -----------

- An obvious question is how is this work related to the work and methods used for Enigma?

ENIGMA [9, Jakubův 2020] differs from our neural precedence recommender especially in the task it deals with:
ENIGMA identifies promising clauses for given clause selection,
while our recommender proposes promising symbol precedences.
The most recent version of ENIGMA, named ENIGMA Anonymous [Jakubův 2020], uses the graph neural network (GNN) architecture proposed in [25], and the relation of our work to this architecture is outlined in section 6 of our paper.
While both ours and ENIGMA GNNs process the input problems in a signature-agnostic manner,
the two GNNs are developed independently and have different architectures.

@@

- Despite the clear improvement over baseline, the percentage gained does not appear
to be too big. It is possible, that the potential effect of better orderings is not
too high, regardless of the optimizations. Can you give some insights for this
line of thought?

It is incredibly difficult to estimate in absolute terms, how large an improvement
one could in our setting on TPTP achieve using some form of "perfect orderings".
However, experiments with random precedences [7] showed that the prover perceptibly responds 
to changes of this parameter and that work on a recommender is worthwhile.

[Jakubův 2020]: Jakubův, J., Chvalovský, K., Olšák, M., Piotrowski, B., Suda, M., Urban, J.: ENIGMA Anonymous: Symbol-Independent Inference Guiding Machine (System Description). In: LNCS. vol. 12167 LNAI, pp. 448–463. Springer (2020). https://doi.org/10.1007/978-3-030-51054-1_29

### 2021-03-31 rebuttal.txt

[Jakubův 2020]: Jakubův, J., Chvalovský, K., Olšák, M., Piotrowski, B., Suda, M., Urban, J.: ENIGMA Anonymous: Symbol-Independent Inference Guiding Machine (System Description). In: LNCS. vol. 12167 LNAI, pp. 448–463. Springer (2020). https://doi.org/10.1007/978-3-030-51054-1_29

----------- Response to Review 2 -----------

- How does your tool behave in the presence of theories (assuming AVATAR is used)?

Both in the training and in the evaluation, AVATAR was disabled and we did not consider problems with theories.
Although, in principle, theory symbols could be subject to our recommender, Vampire treats them differently than the rest  
when constructing a precedence and we did not want to be sidetracked by these specificities.

@@

In this experiment, we have not attempted to control nor analyze the similarity between the problems in the training and test sets.
Splitting the problem set by the domain or the source of the problems is, however, an interesting idea.

----------- Response to Review 3 -----------

- Why do you use the number or iterations of the main loop?

We mainly selected this metric because it is deterministic
and can be measured while other processes are making the computer busy.
Wall-clock time is more sensitive to the compute environment 
and more care needs to be taken to obtain meaningful results commeasureable across multiple runs.
However, the point raised by the reviewer is valid and suggests that using wall clock time as the decisive metric,
if implemented well, may increase the performance of the trained system.

### 2021-03-31 rebuttal.txt

We are very grateful for the attention and care the reviewers took when considering our paper.

----------- Response to Review 1 -----------

- An obvious question is how is this work related to the work and methods used for Enigma?

ENIGMA [9, Jakubův 2020] differs from our neural precedence recommender especially in the task it deals with:
ENIGMA identifies promising clauses for given clause selection,
while our recommender proposes promising symbol precedences for the proof search.
The most recent version of ENIGMA, named ENIGMA Anonymous [Jakubův 2020], uses the graph neural network (GNN) architecture proposed in [25], and the relation of our work to this architecture is outlined in section 6 of our paper.
While both our recommender and ENIGMA use a GNN to process the input problems in a signature-agnostic manner,
the two GNNs are developed independently and have different architectures.

### 2021-03-31 rebuttal.txt

We are very grateful for the attention and care the reviewers took when considering our paper.

----------- Response to Review 1 -----------

- An obvious question is how is this work related to the work and methods used for Enigma?

ENIGMA [9, Jakubův 2020] differs from our neural precedence recommender especially in the task it deals with:
ENIGMA identifies promising clauses for given clause selection,
while our recommender proposes a promising symbol precedence for the proof search.
The most recent version of ENIGMA, named ENIGMA Anonymous [Jakubův 2020],
uses the graph neural network (GNN) architecture proposed in [25],
and the relation of our work to this architecture is outlined in section 6 of our paper.
While both our recommender and ENIGMA use a GNN to process the input problems in a signature-agnostic manner,
the two GNNs are developed independently and their architectures are different.

@@

- Despite the clear improvement over baseline, the percentage gained does not appear
to be too big. It is possible, that the potential effect of better orderings is not
too high, regardless of the optimizations. Can you give some insights for this
line of thought?

It is incredibly difficult to estimate, in absolute terms, how large an improvement
one could in our setting on TPTP achieve using some form of "perfect orderings".
However, experiments with random precedences [7] showed that the prover perceptibly responds 
to changes of this parameter and that work on a recommender is worthwhile.

@@

In this experiment, we have not attempted to control nor analyze the similarity between the problems in the training and test sets.
Splitting the problem set by the domain or the source of the problems is, however, an interesting idea.

----------- Response to Review 3 -----------

- Why do you use the number or iterations of the main loop?

We mainly selected this metric because it is deterministic
and can be measured while other processes are making the computer busy.
Wall-clock time is more sensitive to the compute environment 
and more care needs to be taken to obtain meaningful results commeasureable across multiple runs.
However, the point raised by the reviewer is valid and suggests that using wall clock time as the decisive metric,
if implemented well, could increase the performance of the trained system.

### 2021-03-31 rebuttal.txt

In this experiment, we have not attempted to control nor analyze
the similarity between the problems in the training and test sets.
Splitting the problem set by the domain or the source of the problems is,
however, an interesting idea.

----------- Response to Review 3 -----------

- Why do you use the number or iterations of the main loop?

We mainly selected this metric because it is deterministic and can be
measured while other processes are making the computer busy.  Wall-clock
time is more sensitive to the computing environment and more care needs to
be taken to obtain meaningful results commeasureable across multiple runs.
However, the point raised by the reviewer is valid and suggests that
using wall-clock time as the decisive metric, if implemented well,
could increase the performance of the trained system.

### 2021-04-13 architecture.tex
Remove a superfluous expectation index
Clarify how the expected precedence cost is computed

We extend the notion of cost from symbols to precedences
by taking the sum of the symbol costs
weighted by their positions in the given precedence $\pi$:
\todo[inline]{FB: Consider accessing elements $\pi$ as vector elements $\pi_i$ instead of $\pi(i)$. Keep in mind that $\inv{\pi}$ must be updated as well. The motivation for using $\pi(i)$ is that $\inv{\pi}(i)$ looks clearer than $\inv{\pi}_i$. How about using $(\inv{\pi})_i$? We may also omit the inversion completely.}
\todo{FB: Consider using the terminology of RankNet: $C(\pi) = o_i$, $S(\pi, \rho) = o_{ij}$, $\loss = C_{ij}$}
\begin{equation*} \label{eq:cost_model}
C(\pi) = Z_n \sum_{i=1}^n i \cdot c(\pi(i))% We call the normalization factor Z_n to follow convention from Foundations of Machine Learning, p. 122.
\end{equation*}
$Z_n = \frac{2}{n(n+1)}$ is a normalization factor
that ensures the commensurability of precedence costs across signature sizes.
More precisely, normalizing by $Z_n$ makes the expected value of the precedence cost
independent of the signature size $n$:
\begin{multline*}
\mathbb{E}_\pi [C(\pi)]
= \mathbb{E}_\pi \SquareBracket{Z_n \sum_{i=1}^n i \cdot c(\pi(i))}
= Z_n \sum_{i=1}^n i \cdot \mathbb{E}_{\pi, i} [c(\pi(i))] \\
= Z_n \Parentheses{\sum_{i=1}^n i} \mathbb{E}_i [c(i)]
= \frac{2}{n(n+1)} \frac{n(n+1)}{2} \mathbb{E}_i [c(i)]
= \mathbb{E}_i [c(i)]
\end{multline*}
\todo[inline,author=R2]{In the equations showing that the expected value of the precedence cost is independent of the size of the signature, there is a (minor) problem in the second line: the i occurring in $E_i[c(i)]$ is not defined and probably unneeded if, as hinted by the equations, the expected value of each symbol is the same (which should also be stated somewhere).}

>>>>

We extend the notion of cost from symbols to precedences
by taking the sum of the symbol costs
weighted by their positions in the given precedence $\pi$:
\todo[inline]{FB: Consider accessing elements $\pi$ as vector elements $\pi_i$ instead of $\pi(i)$. Keep in mind that $\inv{\pi}$ must be updated as well. The motivation for using $\pi(i)$ is that $\inv{\pi}(i)$ looks clearer than $\inv{\pi}_i$. How about using $(\inv{\pi})_i$? We may also omit the inversion completely.}
\todo{FB: Consider using the terminology of RankNet: $C(\pi) = o_i$, $S(\pi, \rho) = o_{ij}$, $\loss = C_{ij}$}
\begin{equation*} \label{eq:cost_model}
C(\pi) = Z_n \sum_{i=1}^n i \cdot c(\pi(i))% We call the normalization factor Z_n to follow convention from Foundations of Machine Learning, p. 122.
\end{equation*}
$Z_n = \frac{2}{n(n+1)}$ is a normalization factor
that ensures the commensurability of precedence costs across signature sizes.
More precisely, normalizing by $Z_n$ makes the expected value of the precedence cost on a given problem
independent of the problem's signature size $n$,
provided the expected symbol cost $\mathbb{E}_i [c(i)]$ does not depend on $n$:
\begin{multline*}
\mathbb{E}_\pi [C(\pi)]
= \mathbb{E}_\pi \SquareBracket{Z_n \sum_{i=1}^n i \cdot c(\pi(i))}
= Z_n \sum_{i=1}^n i \cdot \mathbb{E}_\pi [c(\pi(i))] \\
= Z_n \Parentheses{\sum_{i=1}^n i} \mathbb{E}_i [c(i)]
= \frac{2}{n(n+1)} \frac{n(n+1)}{2} \mathbb{E}_i [c(i)]
= \mathbb{E}_i [c(i)]
\end{multline*}
\todo[inline,author=R2]{In the equations showing that the expected value of the precedence cost is independent of the size of the signature, there is a (minor) problem in the second line: the i occurring in $E_i[c(i)]$ is not defined and probably unneeded if, as hinted by the equations, the expected value of each symbol is the same (which should also be stated somewhere).}
